### 2015-08-27 doc/article/article.tex
worked a bit on the wording and minor improvements to mccons

\subsection*{Consensus Problem}

Given $k$ sets of $ m_1, m_2... m_n$ objects, the consensus problem is to find a set of $k$ objects, one per set, minimizing the sum of their pairwise distance. This is modelled as finding the smallest cycle in a complete $k$-partite graph.

% http://stackoverflow.com/questions/17168049/max-weight-k-clique-in-a-complete-k-partite-graph
% http://cstheory.stackexchange.com/questions/30679/k-clique-in-k-partite-graph
% http://cstheory.stackexchange.com/questions/30605/many-one-reduction-from-inequality-problem-to-equality-problem
\noindent The consensus problem is reformulated as the problem of finding a minimal $k$-clique in a complete weighted $k$-partite graph where $k$ is a free parameter. This problem is known to be intractable

\noindent The consensus problem can be transformed into a MIN-SUM \textit{compact location problem} \cite{compact_location}. To reduce it, we add a large positive penalty $M$ to the distance of objects belonging to the same set. This way, any consensus using more than one object belonging to the same set is noncompetitive. Since the MIN-SUM compact location problem is NP-HARD, even for metric distance functions \cite{compact_location}, the use of heuristics is justified.

@@

Most RNA secondary structure prediction tools allow for the exploration of suboptimal secondary structures. This is important because RNA achieve function only with multiple alternating structures \cite{need_subopts}. Also, the experimentally determined structures of reference structures are usually close to the best structure found.

>>>>

\subsection*{Consensus Problem}
% http://stackoverflow.com/questions/17168049/max-weight-k-clique-in-a-complete-k-partite-graph
% http://cstheory.stackexchange.com/questions/30679/k-clique-in-k-partite-graph
% http://cstheory.stackexchange.com/questions/30605/many-one-reduction-from-inequality-problem-to-equality-problem
Given $k$ sets of $m_0, m_1... m_k$ objects, the consensus problem is to find a set of $k$ objects, one per set, minimizing the sum of their pairwise distance.
This is equivalent to the maximum edge-weighted clique problem in a complete $k$-partite graph. This problem is NP-hard and this justifies the use of heuristic methods on larger instances.

%\noindent The consensus problem can be transformed into a MIN-SUM \textit{compact location problem} \cite{compact_location}. To reduce it, we add a large positive penalty $M$ to the distance of objects belonging to the same set. This way, any consensus using more than one object belonging to the same set is noncompetitive. Since the MIN-SUM compact location problem is NP-HARD, even for metric distance functions \cite{compact_location}, the use of heuristics is justified.

@@

Most RNA secondary structure prediction tools allow for the exploration of suboptimal secondary structures. This is important because some RNA achieve function only with multiple structures \cite{need_subopts}. Also, the experimentally determined structures of reference structures are often close to the best structure predicted.
